---
title: "01. Initial data investigation"
author: "Al Xin"
date: "3/27/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
library(tidyverse)
library(xlsx)
```

```{r}
prop <- read.csv("data/residential.csv")
```

At this stage, we can be more selective about the variables to include and filter the columns of our data set. 

```{r}
prop <- prop %>%
  select(
    -pid, 
    -residential_exemption, 
    -book_page, 
    -owner_name:-finished_basement_gross
  )
```

Using the GISID of a building, we can determine whether we have the full set of data on a building (2016-2021). 

For the buildings with less than six observations per unit, we can determine if the building was destroyed or newly constructed by investigating the max and min year observed.

```{r}
gisid_count <- prop %>%
  filter(is_res_code == T) %>%
  group_by(gisid, unit) %>%
  summarize(
    n_assess = n(), 
    yr_max = max(year_of_assessment), 
    yr_min = min(year_of_assessment)
    ) %>%
  arrange(desc(n_assess))

temp <- gisid_count$yr_max == 2021 & gisid_count$yr_min == 2016

gisid_count <-  mutate(
  gisid_count, 
  is_woke = yr_min > 2016, 
  is_broke = yr_max < 2021, 
) %>%
  mutate(is_complete = !(is_woke | is_broke))
```

We can then append this data to the data frame containing property details. 

```{r}
prop_gisid <- inner_join(prop, gisid_count, by = c("gisid", "unit"))
```

```{r}
write.csv(prop_gisid, file = "data/gisid.csv", row.names = F, quote = T)
```
